PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-15 paper/ms.tex
update a few words in intro

While the planetary interpretation clearly faces challenges, there is
no completely satisfactory alternate explanation.  High-latitude
accretion hotspots might produce the observed H$\alpha$ variability,
but require fine-tuning to produce dips of the appropriate duration.
Transits by dust clumps or other dusty features are questionable
because \ptfo\ does not have a detectable infrared (IR) excess
associated with the presence of warm dust \citep[{\it
e.g.},][Figure~18]{yu_tests_2015}.  Low-latitude starspots, hot or
cold, would struggle to produce photometric features as short as some
of the observed dips.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.5\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Timing residuals for \ptfob\ based on a decade of
    monitoring.} Black points are times of dips, minus the indicated
    linear ephemeris.  The phase of the shorter-period signal is
    plotted on the $y$-axis. The star symbol represents the TESS
    ephemeris.  Dips were observed by \citet{van_eyken_ptf_2012},
    \citet{ciardi_followup_2015}, \citet{yu_tests_2015},
    \citet{raetz_yeti_2016}, \citet{onitsuka_multicolor_2017}, and
    \citet{tanimoto_evidence_2020}.  Certain dips ({\it e.g.}, the one
    at phase 0 in mid-2019) are consistent with noise, and were likely
    reported because dips were expected, rather than convincingly
    observed.  Horizontal dashed lines are drawn at $\pm (P_{\rm \ell}
    - P_{\rm s})/P_{\rm s}$, highlighting a possible numerical
    coincidence.  The orbital phase observed by TESS (lower-right) is
    consistent with that of \citet{tanimoto_evidence_2020}.
		\label{fig:o_minus_c}
	}
\end{figure}

@@

The key question is what causes the transient dips. This is
an unsolved problem not only for \ptfo\ but also for the emerging
class of similar young and rapidly rotating M-dwarfs.  Many possible
explanations were discussed by \citet{rebull_rotation_2016},
\citet{david_transient_2017}, \citet{stauffer_orbiting_2017}, and
\citet{zhan_complex_2019}.  Among the {\it disfavored} explanations
are that the dips are caused by
{\it (i)} eclipsing binaries;
{\it (ii)} ``dipper''-flavor Class-I or Class-II disks;
{\it (iii)} eclipses of prominences;
% JNW: why is this one ruled out? Sounds similar to the accretion-hotspot hypothesis.
{\it (iv)} high-latitude accretion hotspots;
{\it (v)} high-latitude starspots;
or
{\it (vi)} dust clouds of plausible composition.
We also view the possibility of {\it (vii)} tidally disrupted
planetary or cometary material to be implausible, given the
synchronicity between dip and rotation periods seen across many
systems.
% JNW Could the material get magnetically locked at the corotation radius?

>>>>

While the planetary interpretation clearly faces challenges, there is
no completely satisfactory alternate explanation.  Low-latitude
starspots, hot or cold, would struggle to produce photometric features
as short as some of the observed dips.  High-latitude accretion
hotspots might produce the observed H$\alpha$ variability, but require
fine-tuning to produce dips of the appropriate duration.  Transits by
dust clumps or other dusty features are questionable because \ptfo\
does not have a detectable infrared (IR) excess associated with the
presence of warm dust \citep[{\it e.g.},][Figure~18]{yu_tests_2015}.
In addition, the sublimation times for dust grains of plausible
composition are quite short \citep{zhan_complex_2019}.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Timing residuals for \ptfob\ based on a decade of
    monitoring.} Black points are times of dips, minus the indicated
    linear ephemeris.  The phase of the shorter-period signal is
    plotted on the $y$-axis. The star symbol represents the TESS
    ephemeris.  Dips were observed by \citet{van_eyken_ptf_2012},
    \citet{ciardi_followup_2015}, \citet{yu_tests_2015},
    \citet{raetz_yeti_2016}, \citet{onitsuka_multicolor_2017}, and
    \citet{tanimoto_evidence_2020}.  Certain dips ({\it e.g.}, the one
    at phase 0 in mid-2019) are consistent with noise, and were likely
    reported because dips were expected, rather than convincingly
    observed.  Horizontal dashed lines are drawn at $\pm (P_{\rm \ell}
    - P_{\rm s})/P_{\rm s}$, highlighting a possible numerical
    coincidence.  The orbital phase observed by TESS (lower-right) is
    consistent with that of \citet{tanimoto_evidence_2020}.
		\label{fig:o_minus_c}
	}
\end{figure}

@@

The key question is what causes the transient dips. This is
an unsolved problem not only for \ptfo\ but also for the emerging
class of similar young and rapidly rotating M-dwarfs.  Many possible
explanations were discussed by \citet{rebull_rotation_2016},
\citet{david_transient_2017}, \citet{stauffer_orbiting_2017}, and
\citet{zhan_complex_2019}.  Among the {\it disfavored} explanations
are that the dips are caused by
{\it (i)} eclipsing binaries;
{\it (ii)} ``dipper''-flavor Class-I or Class-II disks;
{\it (iii)} eclipses of prominences;
{\it (iv)} high-latitude accretion hotspots;
{\it (v)} high-latitude starspots;
or
{\it (vi)} dust clouds of plausible composition.
We also view the possibility of {\it (vii)} tidally disrupted
planetary or cometary material to be implausible, given the
synchronicity between dip and rotation periods seen across many
systems.
